---
title: "Jungle Viability"
author: "Brett Burk"
date: "July 1, 2017"
output: html_document
---
```{r load-in, warning = FALSE, message = FALSE, results = 'asis', quietly = TRUE}
library(httr)
library(jsonlite)
library(lubridate)
library(knitr)
library(dplyr)

folder <- "E:\\Projects\\stratz\\"
# folder <- "C:\\Users\\bmburk\\Dropbox\\stratz\\"

options(stringsAsFactors = FALSE)
# stratzAPI <- "https://apibeta.stratz.com/api/v1/hero"
# stratzAPI <- GET(stratzAPI)
# stratzAPI <- rawToChar(stratzAPI$content)
# stratzAPI <- fromJSON(stratzAPI)
# heroNum <- cbind(do.call("rbind", lapply(stratzAPI, "[[", 1)), do.call("rbind", lapply(stratzAPI, "[[", 3)))
# heroNum <- as.data.frame(heroNum)
# 
# heroNum <- heroNum[order(as.numeric(heroNum$V1)),]
# write.csv(heroNum, paste0(folder, "heroNum.csv"), row.names = F)
# 
# heroNum$V3 <- NA
# for(num in heroNum$V1){
#   stratzAPI <- paste0("https://apibeta.stratz.com/api/v1/hero/directory?heroId=", num)
#   stratzAPI <- GET(stratzAPI)
#   stratzAPI <- rawToChar(stratzAPI$content)
#   stratzAPI <- fromJSON(stratzAPI)
#   heroNum[heroNum$V1 == num, 3] <- round(stratzAPI$heroTimeDetail$events[[1]]$wins/stratzAPI$heroTimeDetail$events[[1]]$matchCount, 3)
# }
# 
# write.csv(heroNum, paste0(folder, "heroNum.csv"), row.names = F)

heroNum <- read.csv(paste0(folder, "heroNum.csv"), stringsAsFactors = F)

options(stringsAsFactors = TRUE)

# Load In
mlr2 <- read.csv(paste0(folder, "MatchLaneRank2.csv"), stringsAsFactors = FALSE)
mlr5 <- read.csv(paste0(folder, "MatchLaneRank5.csv"), stringsAsFactors = FALSE)
mlr8 <- read.csv(paste0(folder, "MatchLaneRank8.csv"), stringsAsFactors = FALSE)
mr <- read.csv(paste0(folder, "MatchRole.csv"), stringsAsFactors = FALSE)

# Rank is mmr
lc <- read.csv(paste0(folder, "LegionCommander.csv"), stringsAsFactors = FALSE)
lc$Lane[lc$Lane == 0] <- "Roaming"
lc$Lane[lc$Lane == 1] <- "Safe Lane"
lc$Lane[lc$Lane == 2] <- "Mid"
lc$Lane[lc$Lane == 3] <- "Offlane"
lc$Lane[lc$Lane == 4] <- "Jungle"

lc$Role[lc$Role == "0"] <- "Core"
lc$Role[lc$Role == "1"] <- "Support"

new.df <- data.frame(matrix(ncol = ncol(lc), nrow = 0))
names(new.df) <- names(lc)

lc$UniqueID <- cumsum(c(0, as.numeric(lc$Time) == 0))[-1]

lc.vs <- read.csv(paste0(folder, "LegionVs.csv"), stringsAsFactors = FALSE)
lc.vs[,c(5, 7:ncol(lc.vs))] <- lc.vs[,c(5, 7:ncol(lc.vs))]/lc.vs[,6]
lc.vs[,5:ncol(lc.vs)] <- round(lc.vs[,5:ncol(lc.vs)], 2)
lc.vs$VsHeroId <- heroNum$V2[match(lc.vs$VsHeroId, heroNum$V1)]
```

Stun
StunDuration
Slow
SlowDuration
Disable
DisableDuration
HpRegen

first.ten <- lc[lc$Time <= 10,]

```{r}
# round(aggregate(lc.vs$Wins, by = list(lc.vs$Rank), summary), 3)
# round(aggregate(lc.vs$Wins, by = list(lc.vs$Rank), sd), 3)

sd.rank.df <- data.frame(rank = 0:9,  
           lower = round(aggregate(lc.vs$Wins, by = list(lc.vs$Rank), mean), 3)[,2] - 2 * round(aggregate(lc.vs$Wins, by = list(lc.vs$Rank), sd), 3)[,2],
           upper = round(aggregate(lc.vs$Wins, by = list(lc.vs$Rank), mean), 3)[,2] + 2 * round(aggregate(lc.vs$Wins, by = list(lc.vs$Rank), sd), 3)[,2])

good.df <- data.frame(hero = character(), winrate = 

for(i in 1:nrow(lc.vs)){
  curr.row <- lc.vs[i,]
  curr.sd <- sd.rank.df[sd.rank.df$rank == curr.row$Rank,]
  # if((curr.row$Wins >= curr.sd$upper|curr.row$Wins <= curr.sd$lower) & curr.row$Count >= 5){
  #   print(paste(curr.row$VsHeroId, "rank:", curr.row$Rank, "count:", curr.row$Count, "Wins:", curr.row$Wins))
  # }
  if(curr.row$Count >= 20){
    if(curr.row$Wins >= curr.sd$upper){
      print(paste(i, "Especially good vs", curr.row$VsHeroId, "rank:", curr.row$Rank, "Count:", curr.row$Count, "Wins:", curr.row$Wins, "Upper:", curr.sd$upper))
    }
    if(curr.row$Wins <= curr.sd$lower){
      print(paste(i, "Especially bad vs", curr.row$VsHeroId, "rank:", curr.row$Rank, "Count:", curr.row$Count, "Wins:", curr.row$Wins, "Lower:", curr.sd$upper))
    }
  }
}
```

HeroId
heroNum

```{r}

```
Check heroes vs normal winrates

good matchups? especially bad matchups?

team comps where she is good?
team comps where especially bad?

Why is she bad at jungle?
+Team networth at 10
+Hero damage
++At ten?
++Overall
+Game lengths long/short?
+Too much physical damage?
+Magical Damage?

Are all jungle heroes bad?
+Can they be offset (stacking?)
